### 2023-01-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@0d987a4a95a9b8ce4a7d52fcc44b70ecdcd52d81 🚀

        {\bfseries 1:}\,Community ecologists are increasingly thinking
probabilistically when it comes to food webs and other ecological
networks. Assuredly, the benefits of representing ecological
interactions as probabilistic events (e.g., how likely are species to
interact?) instead of binary objects (e.g., do species interact?) are
numerous, from a better assessment of the spatiotemporal variation of
trophic interactions to an increase capacity to reconstruct networks
from sparse data. However, probabilities need to be used with caution
when working with species interactions. Indeed, depending on the system
at hand and the method used to build probabilistic networks,
probabilities can have different interpretations that imply different
ways to manipulate them. At the core of these differences lie the
distinction between assessing the likelihood that two groups of
individuals \emph{can} interact and the likelihood that they \emph{will}
interact. This impacts the spatial, temporal, and taxonomic scaling of
interaction probabilities, thus enlightening the need to properly define
them in their ecological context. Published data on probabilistic
species interactions are poorly documented in the literature, which
impedes our ability to use them appropriately. With these challenges in
mind, we propose a general approach to thinking about probabilities in
regards to ecological interactions, with a strong focus on food webs,
and call for better definitions and conceptualizations of probabilistic
ecological networks, both at the local and regional scales.\\%

>>>>

\vfill
Community ecologists are increasingly thinking probabilistically when it
comes to food webs and other ecological networks. Assuredly, the
benefits of representing ecological interactions as probabilistic events
(e.g., how likely are species to interact?) instead of binary objects
(e.g., do species interact?) are numerous, from a better assessment of
the spatiotemporal variation of trophic interactions to an increase
capacity to reconstruct networks from sparse data. However,
probabilities need to be used with caution when working with species
interactions. Indeed, depending on the system at hand and the method
used to build probabilistic networks, probabilities can have different
interpretations that imply different ways to manipulate them. At the
core of these differences lie the distinction between assessing the
likelihood that two groups of individuals \emph{can} interact and the
likelihood that they \emph{will} interact. This impacts the spatial,
temporal, and taxonomic scaling of interaction probabilities, thus
enlightening the need to properly define them in their ecological
context. Published data on probabilistic species interactions are poorly
documented in the literature, which impedes our ability to use them
appropriately. With these challenges in mind, we propose a general
approach to thinking about probabilities in regards to ecological
interactions, with a strong focus on food webs, and call for better
definitions and conceptualizations of probabilistic ecological networks,
both at the local and regional scales.

### 2023-01-28 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@0d987a4a95a9b8ce4a7d52fcc44b70ecdcd52d81 🚀

        {\bfseries 1:}\,Community ecologists are increasingly thinking
probabilistically when it comes to food webs and other ecological
networks. Assuredly, the benefits of representing ecological
interactions as probabilistic events (e.g., how likely are species to
interact?) instead of binary objects (e.g., do species interact?) are
numerous, from a better assessment of the spatiotemporal variation of
trophic interactions to an increase capacity to reconstruct networks
from sparse data. However, probabilities need to be used with caution
when working with species interactions. Indeed, depending on the system
at hand and the method used to build probabilistic networks,
probabilities can have different interpretations that imply different
ways to manipulate them. At the core of these differences lie the
distinction between assessing the likelihood that two groups of
individuals \emph{can} interact and the likelihood that they \emph{will}
interact. This impacts the spatial, temporal, and taxonomic scaling of
interaction probabilities, thus enlightening the need to properly define
them in their ecological context. Published data on probabilistic
species interactions are poorly documented in the literature, which
impedes our ability to use them appropriately. With these challenges in
mind, we propose a general approach to thinking about probabilities in
regards to ecological interactions, with a strong focus on food webs,
and call for better definitions and conceptualizations of probabilistic
ecological networks, both at the local and regional scales.\\%

>>>>

Community ecologists are increasingly thinking probabilistically when it
comes to food webs and other ecological networks. Assuredly, the
benefits of representing ecological interactions as probabilistic events
(e.g., how likely are species to interact?) instead of binary objects
(e.g., do species interact?) are numerous, from a better assessment of
the spatiotemporal variation of trophic interactions to an increase
capacity to reconstruct networks from sparse data. However,
probabilities need to be used with caution when working with species
interactions. Indeed, depending on the system at hand and the method
used to build probabilistic networks, probabilities can have different
interpretations that imply different ways to manipulate them. At the
core of these differences lie the distinction between assessing the
likelihood that two groups of individuals \emph{can} interact and the
likelihood that they \emph{will} interact. This impacts the spatial,
temporal, and taxonomic scaling of interaction probabilities, thus
enlightening the need to properly define them in their ecological
context. Published data on probabilistic species interactions are poorly
documented in the literature, which impedes our ability to use them
appropriately. With these challenges in mind, we propose a general
approach to thinking about probabilities in regards to ecological
interactions, with a strong focus on food webs, and call for better
definitions and conceptualizations of probabilistic ecological networks,
both at the local and regional scales.
